Analysis of 2005--2015 Earthquake Sequence in Northern Iran Using the Visibility Graph Method

### 2016-08-17 seismicity.tex
working...

>>>>

It follows from this that the region of interest is one of significant seismic activity, which goes back centuries. We are, however, interested in the most recent instrumental seismicity. In particular, we focus on events recorded in the last decade, between January 2005 and December 2015. We downloaded a catalog of recorded earthquakes
